\documentclass{acmsiggraph}

\usepackage{parskip}
\usepackage{graphicx}
\usepackage{courier}
\usepackage{footmisc}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{url}
\usepackage{color}
\usepackage{xcolor}
\onlineid{0}

\title{Deriving Depth From a Fixed-Position Variable-Focus Camera}

\author{Tim Horton\thanks{e-mail: hortot2@rpi.edu}\\Rensselaer Polytechnic Institute}

\begin{document}

\maketitle

\section*{Abstract}

Much work has been done regarding the capture of three-dimensional data from the real world into a computer. Some approaches have multiple cameras capturing from different perspectives; others use a grid of known geometry projected onto the scene and measure its deformation.

This paper will explore the possibility of capturing three-dimensional data using a single camera, at a fixed point in space, and without manipulating the scene with projected light or otherwise. Instead, we will focus on the image processing technique required to extract depth information from multiple frames taken with a shallow depth-of-field at different focal distances.

\section{Introduction}

The human brain generally uses perspective information gleaned from having two sensors --- our eyes --- placed at different points in space in order to determine the depth of objects in a scene. However, while the loss of one eye does significantly hinder one's ability to capture depth information, the brain is still able to capture \emph{rough} depth information from other sources.

One such source is the focal blur caused by the fact that the human eye is not a pinhole camera --- it does not have an infinitely small aperture. The brain can separate a scene into layers of depth based on where in its focal range each part of the scene comes into focus. It's this biological approach which we will attempt to reimplement as a computer vision algorithm.

\section{Prior Art}

\section{Implementation}

\section{Algorithm}

\subsection{Breathing Correction}

\subsection{Contrast Detection}

\subsection{Merging and Reduction}

\subsection{Filling}

\section{Visualization}

\subsection{Infinite Depth-of-Field}

\subsection{Anaglyph 3D}

\section{Results}

\subsection{Simple Scene}

\subsection{Complicated Scene}

\subsection{Performance}

\subsection{Analysis \& Known Problems}

\subsubsection{Analysis}

\subsubsection{Breathing Correction}

\subsubsection{Areas of Flat Color}

\subsubsection{Bright Points}

\subsubsection{}

\section{Applications}

\section{Future Work}

\subsection{Optimization of Results}

\subsection{Performance Optimization}

\subsection{Visualization}

\section{Conclusion}

\section{References}

http://www.ncbi.nlm.nih.gov/pubmed/8728981

\end{document}